A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-22 tex-arxiv/article.tex
add preprocess schematic

To create the data, rigid body definitions in the operator software were created for all object to be tracked. These were then streamed on the local network, relayed over \emph{Robot Operating System} (ROS) topics corresponding to each rigid body using a pre-existing package and recorded into a bag file to be converted into a .csv data set.

@@

>>>>

In software, rigid body definitions were created for all object to be tracked. These were then streamed on the local network, relayed over \emph{Robot Operating System} (ROS) topics corresponding to each rigid body using a pre-existing package ROS and recorded into a bag file to be converted into a .csv data set.

@@

\begin{figure}
	\centering
	\fbox{\includegraphics[width=16cm]{../img/preprocess_pipeline.png}}
	\caption{Pre-processing pipeline overview.}
	\label{fig:fig2}
\end{figure}

Figure
